Simulation

### 2022-10-15 Quarto_Simulation/index.qmd
Managed to fix the blocked trellis plot issue

---
title: "Simulation"
author: "Jeremy Selva"
format:
  html:
    theme: 
      light: cerulean 
      dark: cyborg
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: false
    code-fold: show
    code-overflow: scroll
    code-copy: true
    code-tools: true
    code-link: true
    self-contained: false
    smooth-scroll: true
execute: 
  cache: true
---

@@

```{r plots as trellis saturated}
saturation_trellis_table <- DCVtestkit::add_plotly_panel(
  dilution_table = saturation_simulated_database,
  dilution_summary = saturation_dilution_summary,
  grouping_variable = c("ID"),
  sample_name_var = "Sample Name",
  dil_batch_var = "Dilution Batch Name",
  dil_batch_col = c(
    "#377eb8"),
  conc_var = "x",
  conc_var_units = "",
  conc_var_interval = 50,
  signal_var = "y",
  have_plot_title = FALSE
) |> 
  DCVtestkit::convert_to_cog(
    grouping_variable = "ID",
    panel_variable = "panel",
    col_name_vec = "col_name_vec",
    desc_vec = "desc_vec",
    type_vec = "type_vec"
  )

@@

```{r plots as trellis lod}
lod_trellis_table <- DCVtestkit::add_plotly_panel(
  dilution_table = lod_simulated_database,
  dilution_summary = lod_dilution_summary,
  grouping_variable = c("ID"),
  sample_name_var = "Sample Name",
  dil_batch_var = "Dilution Batch Name",
  dil_batch_col = c(
    "#377eb8"),
  conc_var = "x",
  conc_var_units = "",
  conc_var_interval = 50,
  signal_var = "y",
  have_plot_title = FALSE
) |> 
  DCVtestkit::convert_to_cog(
    grouping_variable = "ID",
    panel_variable = "panel",
    col_name_vec = "col_name_vec",
    desc_vec = "desc_vec",
    type_vec = "type_vec"
  )

@@

```{r plots as trellis linear}
linear_trellis_table <- DCVtestkit::add_plotly_panel(
  dilution_table = linear_simulated_database,
  dilution_summary = linear_dilution_summary,
  grouping_variable = c("ID"),
  sample_name_var = "Sample Name",
  dil_batch_var = "Dilution Batch Name",
  dil_batch_col = c(
    "#377eb8"),
  conc_var = "x",
  conc_var_units = "",
  conc_var_interval = 50,
  signal_var = "y",
  have_plot_title = FALSE
) |> 
  DCVtestkit::convert_to_cog(
    grouping_variable = "ID",
    panel_variable = "panel",
    col_name_vec = "col_name_vec",
    desc_vec = "desc_vec",
    type_vec = "type_vec"
  )

>>>>

---
title: "Simulation"
author: "Jeremy Selva"
format:
  html:
    theme: 
      light: cerulean 
      dark: cyborg
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: false
    code-fold: show
    code-overflow: scroll
    code-copy: true
    code-tools: true
    code-link: true
    self-contained: false
    smooth-scroll: true
execute: 
  cache: false
---

@@

```{r plots as trellis saturated}
#| column: screen-inset-right

saturation_trellis_table <- DCVtestkit::add_plotly_panel(
  dilution_table = saturation_simulated_database,
  dilution_summary = saturation_dilution_summary,
  grouping_variable = c("ID"),
  sample_name_var = "Sample Name",
  dil_batch_var = "Dilution Batch Name",
  dil_batch_col = c(
    "#377eb8"),
  conc_var = "x",
  conc_var_units = "",
  conc_var_interval = 50,
  signal_var = "y",
  have_plot_title = FALSE
) |> 
  DCVtestkit::convert_to_cog(
    grouping_variable = "ID",
    panel_variable = "panel",
    col_name_vec = "col_name_vec",
    desc_vec = "desc_vec",
    type_vec = "type_vec"
  )

@@

```{r plots as trellis lod}
#| column: screen-inset-right

lod_trellis_table <- DCVtestkit::add_plotly_panel(
  dilution_table = lod_simulated_database,
  dilution_summary = lod_dilution_summary,
  grouping_variable = c("ID"),
  sample_name_var = "Sample Name",
  dil_batch_var = "Dilution Batch Name",
  dil_batch_col = c(
    "#377eb8"),
  conc_var = "x",
  conc_var_units = "",
  conc_var_interval = 50,
  signal_var = "y",
  have_plot_title = FALSE
) |> 
  DCVtestkit::convert_to_cog(
    grouping_variable = "ID",
    panel_variable = "panel",
    col_name_vec = "col_name_vec",
    desc_vec = "desc_vec",
    type_vec = "type_vec"
  )

@@

```{r plots as trellis linear}
#| column: screen-inset-right

linear_trellis_table <- DCVtestkit::add_plotly_panel(
  dilution_table = linear_simulated_database,
  dilution_summary = linear_dilution_summary,
  grouping_variable = c("ID"),
  sample_name_var = "Sample Name",
  dil_batch_var = "Dilution Batch Name",
  dil_batch_col = c(
    "#377eb8"),
  conc_var = "x",
  conc_var_units = "",
  conc_var_interval = 50,
  signal_var = "y",
  have_plot_title = FALSE
) |> 
  DCVtestkit::convert_to_cog(
    grouping_variable = "ID",
    panel_variable = "panel",
    col_name_vec = "col_name_vec",
    desc_vec = "desc_vec",
    type_vec = "type_vec"
  )
